---
title: "eds-212-day-2"
author: "Julia Parish"
date: "8/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)

```
# Find the derivative expression and slope at the indicated value for: f(x)=x2 at x=3


```{r}

fx <- expression(x^2)

df_dx <- D(expr = fx , name = 'x')

df_dx

x <- 3
eval(expr = df_dx)

```
## Find the derivative expression and slope at the indicated value: P(a)=2(3a+2)^4 −5 at a=1.2
```{r}

Pa <- expression(2 * (3 * a + 2 )^4 - 5)

df_da <- D(expr = Pa , name = 'a')

df_da

a <- 1.2
eval(expr = df_da)


```
## Find the derivative expression and slope at the indicated value: g(t) =  -4t/(t^2+1)^3 at t=0


```{r}

gt <- expression((-4 * t) / (t^2 + 1)^3)

df_dt <- D(expr = gt , name = 't')

df_dt

t <- 0
eval(expr = df_dt)


```

## Find the second derivative with respect to z for G(z)=4.6−1.9z^3. Check your solution by hand.

```{r}

gz <- expression(4.6 - 1.9 * z^3)

dg_dz <- D(expr = gz , name = 'z')

dg_dz

d2g_dz2 <- D(expr = dg_dz , name = 'z')

d2g_dz2

#-1.9 x 3 x 2 

```
## find all partials of the following function:
f(x,y,z)=2x^2^y−3x+1+4z^4^x

```{r}
fxyz <- expression((2 * x^2 * y) - (3 * x) + 1 + (4 * z^4 * x))

df_dx <- D(expr = fxyz , name = 'x')

df_dy <- D(expr = fxyz , name = 'y')

df_dz <- D(expr = fxyz , name = 'z')


```

## Create a plot of the function f(x)=2.4e^−0.05x^sin(x) for x values from -0.5 to +0.5

```{r}
fx <- function(x) {
  
  2.4 * exp(-0.05)^x * sin(x)
  
}

ggplot(data.frame(x = c(-0.5, 0.5)), aes(x = x)) + 
  stat_function(fun = fx)

```



